\begin{thebibliography}{99}
\label{bibliography}
\setlength{\itemsep}{1.5pt plus 2.0pt minus 1.4pt}
\setlength{\parsep}{0pt}
\setlength{\parskip}{0pt}
\vspace{-6pt}
\bibitem{nswtdr} ATLAS New Small Wheel Technical Design Report. \href{http://cds.cern.ch/record/1552862}{\color{blue}\underline{ATLAS-TDR-020}}.
 \href{https://cds.cern.ch/record/2272355}{\color{blue}\underline{ATL-COM-MUON-2017-036}}.
\bibitem{noisy} P.~Giromini {\it et al,} Performance of a Micromegs octuplet in the time  of noise.
 \href{https://cds.cern.ch/record/2277316}{\color{blue}\underline{ATL-COM-MUON-2017-036}}.
\bibitem{noiseless} P.~Giromini  {\it et al,} Performance of a Micromegs octuplet after removing the major cause of noise.
 \href{https://cds.cern.ch/record/2277316}{\color{blue}\underline{ATL-COM-MUON-2017-040}}.
\bibitem{mmfe8} \url{https://twiki.cern.ch/twiki/bin/viewauth/Atlas/NewSmallWheel}.
\bibitem{addc} \url{https://twiki.cern.ch/twiki/pub/Atlas/February_2015_design_reviews/ADDC_document_for_2015_Feb_NSW_review_v1.0.pdf}.
\bibitem{brian} B.~Clark {\it et al,} An Algorithm for Micromegas Segment
 Reconstruction in the Level-1 Trigger of the New Small Wheel. \href{https://cds.cern.ch/record/1706160}{\color{blue}\underline{ATL-COM-UPGRADE-2014-012}}.
\bibitem{steve} S.~Chan et. al. Micromegas Trigger Processor Algorithm Performance in Nominal, Misaligned, and Misalignment
 Corrected Conditions. \href{https://cds.cern.ch/record/2113121}{\color{blue}\underline{ATL-COM-UPGRADE-2015-033}}.
\bibitem{oldart} K.~DiPetrillo  {it et al,} ATL-COM-MUON-2014-069.
\bibitem{koki} Simulation of the ATLAS New Small Wheel (NSW) System
 \href{http://cds.cern.ch/record/2265067}{\color{blue}\underline{ATL-MUON-SLIDE-2017-248}}.
\bibitem{phase2} ATLAS Muon Spectrometer Phase-II Upgrade Technical Design Report. \href{https://cds.cern.ch/record/2270169/}{\color{blue}\underline{ATL-COM-MUON-2017-033}}.
\end{thebibliography}








